---
title: "Brownlows Bets"
author: "celia diaz"
date: "10/16/19"
output: html_document: default
 ---

<!-- We recommend you use git branches -- create a separate branch for each major section i.e. Introduction, Methods, Results, Inferential Results, and Discussion and Conclusions - leave the YAML block untouched until the final merge where you put in your own name !-->

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

 At the first day of class there are 35 students in Math Statistics class and professor Brownlow always proposes this bet to his students "I will wager $2 to your bet of $1 that at least two people in today's class have  the same birthday.  He tells me he has made that bet 1137 times so far. Where do you think his profits are? Discuss this in a markdown document

# Methods

<!--Decide on your methods:  In this section explain the approach you will take to attack the issue --- how will you decide on a likely estimate of professor Brownlow's earnings or losses after 1137 bets. Also explain how you construct a 95% confidence interval about your estimate of his winnings !-->

The way I will do this creating a data set that contains all birthdays. I will run through the bet 1137 times. The sample size of the students is 35. If two birthdays are the same then I will gain a $1. If no two birthdays are the same I will lose a net of $2 on my winnings. 


# Profit Estimate

<!--Explain and display the results of your method of coming up with the estimate of professor Brownlows betting!-->
```{r}
bdays = 1:365
Bsamples = vector('numeric')
TotalDollars = 0
saveDollars = vector ('numeric')

```
run the simulation 1137 times
```{r}


saveDollars=vector('numeric')
for (loop in 1:1000) {
  
TotalDollars = 0
for (i in 1:1137){
Bsamples = sample (bdays, 35, replace = TRUE)
if (length (unique(Bsamples)) == 35) {
  TotalDollars = TotalDollars -2
} else {
  TotalDollars = TotalDollars +1
}
}
saveDollars[loop] = TotalDollars }

hist(saveDollars)
print(mean(saveDollars))

```
In the above histogram we found that the mean average was $503. 
The total dollars made is $549. 




# Confidence interval of Brownlows earning

<!--Explain and display your method of coming up with a 95% confidence interval of  professor Brownlows-->
using resampling I found the average was $503.The total dollars made is $549.

```{r}
stdevDollars = sd(saveDollars)
meanDollars= mean(saveDollars)
CI = c(meanDollars-2*stdevDollars, meanDollars+2*stdevDollars) 

print(paste(CI[2],CI[1]))
```
This confidence interval means that we are 95% confident that Dr. Brownlow will make anywhere between $116.00 and $426.00 when taking bets from his students.


# Discussion and Conclusion

<!--Discussion and conclusion here.  If professor Brownlow is consistantly making or losing money how could he change his payout so that his profits center on zero?  Also discuss what size his class should be in order to have his current scheme balance at zero profit.!-->

```{r}
saveDollars=vector('numeric')
for (loop in 1:1000) {
  
TotalDollars = 0
classsize= 29
for (i in 1:1137){
Bsamples = sample (bdays, 35, replace = TRUE)
if (length (unique(Bsamples)) == 35) {
  TotalDollars = TotalDollars -4.5
} else {
  TotalDollars = TotalDollars +1
}
}
saveDollars[loop] = TotalDollars }

hist(saveDollars)
print(mean(saveDollars))

```

In order for Brownlow"s profits to break even at zero we would have to change the amount to 4.5. This would allow Brownlow's profits to remain at zero.
His class size should be 29 in order to have his cureent balance remain at zero or break even.
